---
title: 'Peer-reviewd Assignment 1: Leaflet and R Markdown'
author: "Ali Pourkhesalian"
date: "23/09/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Summary
This document is generated by R Markdown as the peer-graded assingment in Developing Data Products course. The Document conains a map using `leaflet()`.  

## Assignment
The tasks to be carried out in this assignment are as follow:  

1. Create a web page using R Markdown that features a map created with Leaflet.  

2. Host your webpage on either GitHub Pages, RPubs, or NeoCities.  

3. Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity! 

```{r theMap , message=FALSE, comment='', echo=FALSE, warning=FALSE}
library(dplyr)
library(leaflet)
myMap <- leaflet()%>%
  addTiles() 
  
myMap <- myMap %>% 
  addMarkers(lat = -32.884320, lng= 151.728865, 
             popup = "Ali's office")
myMap
```

## Appendix A
The R Markdown file of this document along with the knited html file can be found [here](https://github.com/pourkhesalian/Developing-Data-Products-Assignment-1)